\documentclass[11pt]{IEEEtran}
\usepackage[left=1.5in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% DOC START %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\onecolumn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%% REMOVE CHECK SECTION %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\singlespacing
\input{Checklist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% END REMOVE CHECK SECTION %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\doublespacing

\input{titlepage}
\pagenumbering{roman}
\clearpage
\pagenumbering{arabic}

\clearpage
\section{Section 1}
Companies like SambaNova are at the forefront of this hardware technology, creating chips which can support AI models with up to 5 trillion parameters [4]; however, in order for this impressive technology to become trending, manufacturers need to overcome a host of challenges blocking the next generation of AI fueled technology.  While the aforementioned processors at SambaNova are undoubtedly powerful, the lack of software support for most data flow architectures is creating a void between what's possible, versus what's practical.  Data Flow Architectures have the potential to provide immense compute capability for the field of AI and Machine Learning; however the fledgling software ecosystem to support this architecture creates a unique challenge for its practical use, thus stifling its potential mass consumerization.  More traditional computer architectures, like the Von Neumann CPU architecture and GPU architecture, have a rich software backbone making it a more pragmatic choice for many companies with products the AI/ML space.  Overcoming the current nascent software landscape will be a necessary step in the future of data flow architectures for AI/ML applications. 

\section{Section 2}
Companies like SambaNova are at the forefront of this hardware technology, creating chips which can support AI models with up to 5 trillion parameters [4]; however, in order for this impressive technology to become trending, manufacturers need to overcome a host of challenges blocking the next generation of AI fueled technology.  While the aforementioned processors at SambaNova are undoubtedly powerful, the lack of software support for most data flow architectures is creating a void between what's possible, versus what's practical.  Data Flow Architectures have the potential to provide immense compute capability for the field of AI and Machine Learning; however the fledgling software ecosystem to support this architecture creates a unique challenge for its practical use, thus stifling its potential mass consumerization.  More traditional computer architectures, like the Von Neumann CPU architecture and GPU architecture, have a rich software backbone making it a more pragmatic choice for many companies with products the AI/ML space.  Overcoming the current nascent software landscape will be a necessary step in the future of data flow architectures for AI/ML applications. 

\begin{thebibliography}{00}

\bibitem{b1} SoftwareMill, "Technology Trends," SoftwareMill Blog. [Online]. Available: https://softwaremill.com/technology-trends/. [Accessed: 9-26-2023].
.

\bibitem{b2} "Microservices usage worldwide 2020, by organization size," Statista, 2020. [Online]. Available: https://www.statista.com/statistics/1236823/microservices-usage-per-organization-size/. [Accessed: 9-27-2023].


\bibitem{b3} A. Bitar - Groq, "Groq’s Software-Defined Hardware for Dataflow Compute," YouTube, 27 Feb. 2021. [Video]. Available: https://www.youtube.com/watch?v=nP\_9lkDsD-E\&t=919s. [Accessed: 9-26-2023].

\bibitem{b4} E. Gent, "SambaNova’s New Chip Means GPTs for Everyone," IEEE Spectrum, [Online]. Available: https://spectrum.ieee.org/ai-chip-sambanova. [Accessed: 09-25-2023].

\end{thebibliography}


\end{document}
